Need a good title.

### 2017-12-08 ms.tex
pushing table

\begin{align}
Z^{C} & = BS Z ,
\end{align}

where $BS$ is an $b \times s$ matrix of branch--species relation.

\ml{for correlated intercept and slope it is $Z^{C} = Kron(BS,diag(repterm))^T * Z$}

@@

We generate test data using a simple glmm framework that varies in complexity in random effect. All simulations and fits were performed with R.

>>>>

\begin{equation}
Z^{C}_{i} = (BS \bigotimes I_{q_i \times s})^T Z_{i} ,
\end{equation}

where $BS$ is an $b \times s$ matrix of branch--species relations; $I$ is an identity matrix size $q_i \times s$; $q_i$ is the number of columns contributed by $Z_i$; s is the number of sites; and  $\bigotimes$ is the Kronecker product \ml{cite kronecker}.

@@

\begin{tabular}{|c|c|c|}
\hline
Type of RE	& Formula	& Platform	\\
\hline
Single site intercept										&	1 \mid sp						& gls, lme4 \\
Single site intercept and uncorrelated slopes		&  1 \mid sp + X \mid sp		& lme4 \\
Single site intercept and correlated slopes 			& 1 + X \mid sp					& lme4 \\
\hline
Multiple site intercept 									&  1 \mid sp 						& pez, lme4 \\
Multiple site intercept and uncorrelated slopes 	&  1 \mid sp + X \mid sp 		& pez, lme4 \\
Multiple site intercept and uncorrelated slopes 	& 	1 + X \mid sp					& lme4 \\
ditto with site interaction								& ditto above \mid sp:site		& ditto above \\
\hline

\end{tabular}
\\

We generate test data using a simple glmm framework that varies in complexity in random effect described in Table 1 \ml{macro this}. All simulations and fits were performed with R.
